\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{multicol}

% Page margins
\geometry{margin=0.5in}

% No page numbering
\pagenumbering{gobble}

% Define colors
\definecolor{darkblue}{RGB}{0,0,139}

% Hyperlink settings
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue
}

% Define section formatting
\titleformat{\section}
{\normalfont\Large\bfseries\color{darkblue}}
{}{0em}{}

% Define subsection formatting
\titleformat{\subsection}
{\normalfont\large\bfseries\color{darkblue}}
{}{0em}{}

% Define subsubsection formatting
\titleformat{\subsubsection}
{\normalfont\normalsize\bfseries\color{darkblue}}
{}{0em}{}

% Set spacing before and after sections
\titlespacing*{\section}{0pt}{10pt}{5pt}
\titlespacing*{\subsection}{0pt}{8pt}{4pt}
\titlespacing*{\subsubsection}{0pt}{6pt}{3pt}

\begin{document}

% Title/Header
\begin{center}
     \href{https://dev-trilok.github.io/portfolio/}{\Huge \textbf{\textcolor{black}{Triloknath J Nalawade}}} \\
    \vspace{0.1in}
    \href{mailto:trilokmhl@gmail.com}{trilokmhl@gmail.com} $\cdot$ \href{tel:+919960654964}{(+91) 9960654964}
 $\cdot$ \href{https://linkedin.com/in/triloknath-nalawade/}{Linkedin} $\cdot$ \href{https://dev-trilok.github.io/portfolio/}{GitHub}
\end{center}

% Education
\section*{Education}
\textbf{Master of Computer Application (MCA)}, MES Institute of Management and Career Course, Pune \\
SGPA: 8.2 \hfill June 2019 -- May 2022

% Experience
\section*{Experience}
\begin{itemize}[leftmargin=*]
    \item \textbf{Software Developer}, Aloha Technology Pvt Ltd \hfill August 2021 -- Current
    \begin{itemize}[leftmargin=*]
        \item Contributed to the development of SAAS US Healthcare Projects as part of a team, Worked on both frontend and backend using .NET MVC, Core, and ASP.NET, with  SQL Server.
        \item Worked on the integration of AWS cloud services like S3, Lambda, SNS, and CloudWatch etc.
        \item Worked on implementing third-party integrations with DevExpress, Kendo UI, Form.Io forms, Signal-R, and Zoom API.
        \item Gained knowledge of healthcare billing (EDI 837 and 835) and double-entry accounting systems.
    \end{itemize}

    \item \textbf{Development Intern}, Hk International Pvt Ltd \hfill June 2020 -- July 2020 \
    \begin{itemize}[leftmargin=*]
        \item Designed and hosted a WordPress E-commerce project for a startup.
    \end{itemize}

    \item \textbf{Development Intern}, I-Logic Software Solution, Sangli \hfill May 2019 -- June 2019 \
    \begin{itemize}[leftmargin=*]
        \item Developed a .NET WindowsForms CRUD operations application with SQL Server.
    \end{itemize}
\end{itemize}


% Projects
\section*{Projects}
\begin{itemize}[leftmargin=*]
    \item \textbf{Super Dairy - Dairy Management System} \href{https://github.com/Dev-Trilok/SuperDairy}{Source code} \\
    A Progressive Web Application (PWA) developed using .NET Core MVC and SQL Server. The system allows admin staff to log milk collections from customers, while customers can track their milk and generate reports.

    \item \textbf{DrCarCare - Car Servicing Management System} \href{https://github.com/Dev-Trilok/DrCarCare-Admin-Dashboard}{Source code} \\
    A web application built with React, Material UI, and Firebase. This system tracks car servicing activities.

    \item \textbf{Palavi- Restaurant Management System} \href{https://github.com/Dev-Trilok/Palavi-Online-Resto}{Source code} \\
    A food ordering web application developed with Node.js, Express.js, Tailwind CSS, and MongoDB. Utilized socket.io for real-time order tracking and BCryptJs for password encryption.
\end{itemize}

% Skills
\section*{Skills}
\begin{itemize}[leftmargin=*]
     \textbf{Backend :} ASP.NET, .NET MVC, WebAPI, C\#, VB.NET \\
    \textbf{Frontend :} HTML, CSS, Bootstrap, Tailwind CSS \\
    \textbf{Database:} MS SQL Server \\
    \textbf{JavaScript Ecosystem:} jQuery, ReactJS, Node.js \\
    \textbf{Tools and Technologies:} Git, GitHub, SVN, Visual Studio, VS Code, Postman \\
    \textbf{Additional Languages:} Basic proficiency in Java and Python
\end{itemize}




% Achievements
\section*{Achievements}
\begin{multicols}{2}
\begin{itemize}[leftmargin=*]
    \item \href{https://www.hackerrank.com/profile/trilokmhl}{Hackerrank} 4-star Badge in Java, 2-star in Javascript
    \item \href{https://www.hackerrank.com/profile/trilokmhl}{Hackerrank} Verified Skills - React(Basic)
\end{itemize}
\end{multicols}
% Certificates
\section*{Certificates}
\begin{itemize}[leftmargin=*]
    \item Coursera - Python for Everybody  , Programming Foundation with JavaScript, Html \& Css
   % \item CodeDamn - MongoDB Fundamentals With Node.js
\end{itemize}



\end{document}
